### 2019-03-25 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

\section{Design of Adaptive Model Predictive Control}
We designed a Model Predictive Controller that can make the ATLASCAR2 maintain a desired velocity and stay in the middle of center lane. We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval. Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller. In practice, at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions. Once updated, the model and the conditions remain constant over the prediction horizon. In motion planning that uses adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change. We used an approach that takes advantage of the ability of MPC to handle constraint explicitly. Figure \ref{fig:flowchart} shows a conditional state machine designed for higher-level behavior planning.

% FLOWCHART
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/flowchart/flowchart.pdf}
	\caption{Behaviour planning conditional flowchart.}
	\label{fig:flowchart}
\end{figure}

@@

\section{Simulation Results}
The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three simulation examples. We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$. In all simulations, the distance between the front and rear axles is $C_L=\SI{5}{m}$ and the width of the vehicle is $C_W=\SI{2}{m}$. The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change. Moreover we are using a constant reference signal for the velocity of $v=\SI{20}{m/s}$ ($\approx\SI{72}{km/h}$).
Blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, \ref{fig:braking} are known only at the end of the simulations.

\subsection{One Moving Obstacle - Right Overtaking}
In this first simulation
(Figure \ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane). In other words if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing. If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed. In this simulation only the first three constraints are necessary because there is space for the overtaking without braking (the fourth and fifth constraints don't change).

% ONE MOVING OBSTACLE
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_start.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_end.pdf}
	\end{minipage}
	\caption{Simulation of right overtaking with one moving obstacle that moves in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_one_obstacle}
\end{figure}

% RESULTS ONE MOVING OBSTACLE
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_one_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle illustrated in Figure \ref{fig:obstacleAvoidance_one_obstacle}.}
	\label{fig:components_one_moving_obstacle}
\end{figure}

% ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
\begin{algorithm}%[b]
	\caption{Right Overtaking if an obstacle is detected}
	\small
	\begin{algorithmic}[1]
		\Function{RightOvertaking}{car, obstacle, road}
		\State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
		\State obsYrr = obstacle.RearRightSafeY;
		\State obsXrr = obstacle.RearRightSafeX;
		\If{ATLASCAR2 is behind the obstacle} 
		\If{ATLASCAR2 is in the adjacent lane}
		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
		\Else
		\State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$;
		\State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;
		\EndIf
		\Else
		\If{ATLASCAR2 is parallel to the obstacle}
		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
		\Else
		\State $cS \gets 0$; $cI \gets W/2$;
		\EndIf
		\EndIf
		\State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
		\EndFunction
	\end{algorithmic}
	\label{alg:rightOvertaking}
\end{algorithm}

% OVERALL SCHEME ONE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
	\caption{Overall procedure scheme moving obstacle avoidance.}
	\label{fig:MovingObstacleAvoidance}
\end{figure}
%
\subsection{Multiple Moving Obstacles}
For a second test, additional obstacles were added to make the scenario more complex (Figure \ref{fig:obstacleAvoidance_random}).
% MULTIPLE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
	\end{minipage}
	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
	\label{fig:obstacleAvoidance_random}
\end{figure}

The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road. If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane. We also hypothesized that the obstacles move at different speeds but that they are initially at a common distance; they can have a uniform motion or a uniformely accelerated motion. In case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation. The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario.

% SIX MOVING OBSTACLES
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_6.pdf}
	\end{minipage}
	\caption{Simulation of overtaking with six moving obstacles that moves in the opposite direction with respect the vehicle.}
	\label{fig:obstacleAvoidance_six_obstacles}
\end{figure}

% RESULTS SIX MOVING OBSTACLES
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_six_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of overtaking with six moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_six_obstacles}.}
	\label{fig:components_six_moving_obstacles}
\end{figure}

\subsection{No Overtaking}
%NO OVERTAKING
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_4.pdf}
	\end{minipage}
	\caption{Simulation of no overtaking with three moving obstacles that move in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_no_overtaking}
\end{figure}

% RESULTS NO OVERTAKING
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_no_overtaking}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_no_overtaking}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of no overtaking with three moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_no_overtaking}.}
	\label{fig:components_no_overtaking}
\end{figure}

\subsection{Vehicle Braking and Obstacles Overtaking}
Finally we have improved the code related to the mixed Input/Output constraints so that in the case there are 3 obstacles that block the road and drive at a lower speed than the ATLASCAR2, the velocity of the vehicle decreases in order to prevent the collision. Figure \ref{fig:braking} depicts a simulation in which there are 3 obstacles at the same $x$-coordinate. Two obstacles have a constant speed of \SI{8}{m/s} while the one on the left lane of \SI{15}{m/s}.
In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front. The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame). In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance. In particular three parameters have been identified as the key
factors computing the safe distance between cars:
\begin{itemize}
	\item detection range of the ATLASCAR2;
	\item velocities of the vehicle and the obstacle;
	\item distance between the cars.
\end{itemize}

>>>>

\section{Design of Adaptive Model Predictive Control}
We designed a Model Predictive Controller that can make the ATLASCAR2 maintain a desired velocity and stay in the middle of center lane. We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval. Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller. In practice, at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions. Once updated, the model and the conditions remain constant over the prediction horizon. In motion planning that uses adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change. We used an approach that takes advantage of the ability of MPC to handle constraint explicitly. Figure \ref{fig:flowchart} shows a conditional state machine designed for higher-level behavior planning.
% FLOWCHART
\begin{figure}[!b]
	\centering
	\includegraphics[width=\textwidth]{../figure/flowchart/flowchart.pdf}
	\caption{Behaviour planning conditional flowchart.}
	\label{fig:flowchart}
\end{figure}

@@

\section{Simulation Results}
The performances of the proposed adaptive MPC based vehicle control method are demonstrated in four simulation examples. We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$. In all simulations, the distance between the front and rear axles is $C_L=\SI{5}{m}$ and the width of the vehicle is $C_W=\SI{2}{m}$. The saturation ranges of the control inputs are: the steering angle rate of change lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change. Moreover we are using a constant reference signal for the velocity of $v=\SI{20}{m/s}$ ($\approx\SI{72}{km/h}$).
Note that the blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, 	\ref{fig:obstacleAvoidance_six_obstacles}, \ref{fig:obstacleAvoidance_no_overtaking} and \ref{fig:braking} are known only at the end of the simulations but we have decided to report the entire trajectory that the vehicle will perform in every frame. The overall framework for a multiple moving obstacle avoidance is depicted in the Figure \ref{fig:MovingObstacleAvoidance}.
% OVERALL SCHEME ONE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
	\caption{Overall procedure scheme moving obstacle avoidance.}
	\label{fig:MovingObstacleAvoidance}
\end{figure}

All the simulations are done in MATLAB and Simulink. MATLAB is used for loop-shaping. Simulink is used as a testing environment.  Moreover, the MATLAB Model Predictive Toolbox is used. The controller will be tested in the same Simulink environment as the classical controller. Note that all these blocks have been implemented through the S-functions (types of dynamically linked subroutines for Simulink).

\subsection{One Moving Obstacle - Right Overtaking}
In this first simulation
(Figure \ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane). In this example the obstacle has a constant speed of \SI{8}{m/s} and moves in the same direction as the ATLASCAR2. We assume that the LIDAR sensor can detect an obstacle \SI{30}{m} in front of the vehicle.
The red dashed block around the obstacle represents a safe zone used to evaluate the restrictions so that, even if there is a small margin of error in the manuever, there is always a safe distance between the ATLASCAR2 and the nearby vehicle.
% ONE MOVING OBSTACLE
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_start.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_end.pdf}
	\end{minipage}
	\caption{Simulation of right overtaking with one moving obstacle that moves in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_one_obstacle}
\end{figure}

Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed.
% ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
\begin{algorithm}[!h]
	\caption{Right Overtaking if an obstacle is detected}
	\small
	\begin{algorithmic}[1]
		\Function{RightOvertaking}{car, obstacle, road}
		\State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
		\State obsYrr = Obstacle.RearRightSafeY;
		\State obsXrr = Obstacle.RearRightSafeX;
		\If{ATLASCAR2 is behind the obstacle} 
		\If{ATLASCAR2 is in the adjacent lane}
		\State $cS \gets 0$; $cI \gets \text{obsYrr}$; \label{line:safety_zone}
		\Else
		\State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$; \label{line:corner1}
		\State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;\label{line:corner2}
		\EndIf
		\Else
		\If{ATLASCAR2 is parallel to the obstacle}
		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;\label{line:safety_zone_parallel}
		\Else
		\State $cS \gets 0$; $cI \gets W/2$;\label{line:inactive}
		\EndIf
		\EndIf
		\State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
		\State \text{Update matrices $\vec{E},\vec{F}$ and $\vec{G}$}
		\EndFunction
	\end{algorithmic}
	\label{alg:rightOvertaking}
\end{algorithm}

In other words the constraints are evaluated as follows:
\begin{itemize}
	\item if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint (line \ref{line:safety_zone});
	\item otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing (lines \ref{line:corner1} and \ref{line:corner2});
	\item if the vehicle is parallel to the obstacle (line \ref{line:safety_zone_parallel}), it  uses the safety zone as the constraint;
	\item finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane (line \ref{line:inactive}).
\end{itemize}

In this simulation only the first three constraints are necessary because there is enough space for the overtaking without braking (the fourth and fifth constraints don't change). The first two constraints are constant and represent the left and right boundary of the road (upper and lower bound on the $y$-coordinate). The third constraint is useful to define a region where the vehicle can navigate; it consists of two parameters ($cS$ and $cI$) that are calculated in the algorithm depending on where the vehicle is located with respect to the obstacle. After calculating these parameters, the matrices $\vec{E}$, $\vec{F}$ and $\vec{G}$ are updated so that the MPC can process the new optimal input.

Finally we can analyze time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle. Figures \ref{fig:longitudinal_one_moving} and \ref{fig:lateral_one_moving} illustrate the longitudinal and lateral position of the vehicle with respect to time, showing a constant trend with respect to the $x$ component, while a shift from 0 can be noted regarding the $y$ coordinate due to the overcoming of the obstacle. 
To confirm a uniform trend, the speed of the ATLASCAR2 remains fairly constant. Obviously it is possible to note from Figure \ref{fig:velocity_one_moving} that the velocity decreases very little during the first part of the overtaking phase, and then come back to the cruising speed in the second part. Instead from the remaining Figures \ref{fig:throttle_one_moving}, \ref{fig:delta_one_moving} and \ref{fig:theta_one_moving} we can observe that the throttle $T$ and the steering angle $\delta$ respect the limits we imposed while the heading angle $\theta$ is used to describe the direction the ATLASCAR2 is pointing.
% RESULTS ONE MOVING OBSTACLE
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_one_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle illustrated in Figure \ref{fig:obstacleAvoidance_one_obstacle}.}
	\label{fig:components_one_moving_obstacle}
\end{figure}

%
\subsection{Multiple Moving Obstacles}
For a second test, additional obstacles were added to make the scenario more complex like in a real highway.

Initially we assumed that the obstacles were located at a distance greater than the LIDAR detection range which is \SI{30}{m}. In this way every time the vehicle overtakes a car, it applies the inactive constraints to go back to the center lane.

This situation is represented in Figure \ref{fig:obstacleAvoidance_random}
where there are three different scenarios with $N = 2,3 \text{ and } 4$ moving obstacles that drive with a constant velocity of \SI{8}{m/s} in the opposite direction with respect to the ATLASCAR2. The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road. If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
% MULTIPLE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
	\end{minipage}
	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
	\label{fig:obstacleAvoidance_random}
\end{figure}

In the Figure \ref{fig:obstacleAvoidance_six_obstacles} we also hypothesized there are six moving obstacles that can drive at different speeds but initially they are at a common distance; they can have a uniform motion or a uniformely accelerated motion. We also improved the code infact in case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation. The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario. 
% SIX MOVING OBSTACLES
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_6.pdf}
	\end{minipage}
	\caption{Simulation of overtaking with six moving obstacles that moves in the opposite direction with respect the vehicle.}
	\label{fig:obstacleAvoidance_six_obstacles}
\end{figure}

Also in this case we reported time signals of the ATLASCAR2 in the simulation with six moving obstacles (Figure \ref{fig:components_six_moving_obstacles}). The most articulated scenario makes the signals more complex with respect to time. However, we can see that the speed is just under \SI{20}{m/s} while the inputs continue to respect the imposed boundaries. Note that the vehicle manages to overcome all the obstacles without encountering any difficulty since there is always an empty lane.
% RESULTS SIX MOVING OBSTACLES
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_six_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_six_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of overtaking with six moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_six_obstacles}.}
	\label{fig:components_six_moving_obstacles}
\end{figure}

\subsection{No Overtaking}
We have seen that as long as there is always a free lane, the obstacle avoidance algorithm works correctly. In the case that there are too many obstacles on the road, which do not allow overtaking, the vehicle must adapt to the situation and it must slow down in order not to collide. In the algorithm that we have developed it is possible to calculate two other restrictions which permit this deceleration in the case that it is strictly necessary. To better understand how these restrictions change the speed and deceleration of the ATLASCAR2, we simulated a scenario (Figure \ref{fig:obstacleAvoidance_no_overtaking}) in which there are 3 obstacles at an initial distance of \SI{35}{m} occupying the 3 different lanes, all with the same $x$-coordinate and the same velocity of \SI{8}{m/s}. When these obstacles enter in the vehicle's detection range, it checks whether there is enough space to perform the overtaking maneuver by calculating the distance between the obstacles. Noting that it is not possible to overtake, our vehicle must decelerate in order not to crash into the nearest car. To do this, the MPC must take into account the position of the vehicle $x_\text{min}$ and the position of the closest obstacle $x_\text{max}$.
%NO OVERTAKING
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_4.pdf}
	\end{minipage}
	\caption{Simulation of no overtaking with three moving obstacles that move in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_no_overtaking}
\end{figure}
